\documentclass{report}

\usepackage{amssymb}
\begin{document}
\section{High Energy Experiments}

exploring which (x, $Q^2$) region
\begin{itemize}
    \item Elastic scattering
    \item Inclusive inelastic scattering
    \item Deep Inelastic scattering (DIS)
\end{itemize}


\subsection{Low and Medium energy experiments}
Nucleon structure function
\begin{itemize}
    \item $F_1^\gamma(x, Q^2) = \frac{1}{2}\sum Q_q^2 \left[q(x, Q^2) + \bar{q}(x, Q^2)\right]$
    \item $F_1^{\gamma Z}(x, Q^2) = \sum Q_q g_V^q \left[q(x, Q^2) + \bar{q}(x, Q^2)\right]$
    \item $F_3^{\gamma Z}(x, Q^2) = 2\sum Q_q g_A^q \left[q(x, Q^2) - \bar{q}(x, Q^2)\right]$
    \item The third electron-quark neutral-current effective couplings: $2C_{3u} - C_{3d}$
	$$ L_{NC}^{eq} = \frac{G_F}{\sqrt{2}}\left[ C_{1q}\bar{e}\gamma^{\mu}\gamma_5e\bar{q}\gamma_\mu q 
	+ C_{2q}\bar{e}\gamma^{\mu}e\bar{q}\gamma_\mu\gamma_5q
	+ C_{3q}\bar{e}\gamma^{\mu}\gamma_5e\bar{q}\gamma_\mu\gamma_5q\right]$$

	where $C_{3q} \equiv -2c_A^e c_A^q$ with $c_A^{e(q)}$ the axial weak charge of the electron (quark)
	$$ C_{1u} = -\frac{1}{2} + \frac{4}{3}\sin^2\theta_W    \quad
	C_{2u} = -\frac{1}{2} + 2\sin^2\theta_W \quad
	C_{3u} = \frac{1}{2} 
	$$
	$$ C_{1d} = \frac{1}{2} - \frac{2}{3}\sin^2\theta_W    \quad
	C_{2d} = \frac{1}{2} - 2\sin^2\theta_W \quad
	C_{3d} = -\frac{1}{2} 
	$$
    \item Muonic $C_{3q}$ was measured at CERN in 1980 to be: $2C_{3u}^{\mu q} - C_{3d}^{\mu q} = 1.57 \pm 0.38$: A. Argento et al. Electroweak Asymmetry in Deep Inelastic Muon - Nucleon Scattering.
Phys. Lett. B, 120:245, 1983.
    \item P2 experiment at Mainz will measure $C_{1q}$
    \item SoLID at JLab will measure $C_{2q}$
    \item $g_{AV}^{eq}, g_{VA}^{eq}, g_{AA}^{eq}$ are new notation of $C_{1q}, C_{2q}, C_{3q}$ with higher-order process-specific correction (possible BSM process), they are independent of the processes in which they are measured
\end{itemize}


\section{Standard Model}
\begin{itemize}
    \item Higgs boson:
	\begin{itemize}
	    \item M. Aaboud et al. Observation of H $\rightarrow$ $b\bar{b}$ decays and V H production with the ATLAS detector. Phys. Lett. B, 786:59–86, 2018.
	    \item  A. M. Sirunyan et al. Observation of Higgs boson decay to bottom quarks. Phys. Rev. Lett., 121(12):121801, 2018.
	\end{itemize}

    \item muon g-2:
	\begin{itemize}
	    \item B. Abi et al. Measurement of the Positive Muon Anomalous Magnetic Moment to 0.46
ppm. Phys. Rev. Lett., 126(14):141801, 2021.
	\end{itemize}

    \item Proton weak charge
	\begin{itemize}
	    \item Qweak: D. Androić et al. Precision measurement of the weak charge of the proton. Nature, 557(7704):207–211, 2018.
	\end{itemize}

    \item{Parton Distribution Function (PDF)}
	\begin{itemize}
	    \item MMHT2014
	    \item CT18
	    \item CJ15
	\end{itemize}
\end{itemize}

\section{Physical Problems}
\begin{itemize}
    \item Are leptons and quarks are made of smaller particles? or are they point-like (must elemental particles be point-like? Is it possible for elementary particle to have some structure?)
    \item Are there new interactions at higher energy scale that we never reach?
    \item At which energy scale, we can unify strong and EW interaction?
    \item Neutrino masses?
    \item Dark matter and dark energy
    \item Can we reduce the number of parameters of SM?
    \item How and where to unify gravity 
\end{itemize}

\subsection{Nuclear Physics}
\begin{itemize}
    \item Is the nucleon immutable
    \item Origin of saturation
    \item Behavior at very high density (neutron star) -- transition from hadronic to quark matter
\end{itemize}

\section{Review}
\begin{itemize}
    \item Two Photon Exchange (TPE): J. Arrington, P. G. Blunden, and W. Melnitchouk. Review of two-photon exchange in electron scattering. Prog. Part. Nucl. Phys., 66:782–833, 2011.
\end{itemize}
\end{document}
