\chapter{Terminology}
\begin{description}
    %%%%%%%%% A %%%%%%%%%%% 
    \item [adjoint representation]
    \item [analyticity]
    \item [associativity of addition and multiplication]    
	$a+(b+c) = (a+b)+c$   , and $a\cdot(b\cdot c)=(a\cdot b)\cdot c$
    \item [bilinear]	In QFT, a bilinear term means it has exactly two
	fields. Such as:
	\[ \mathcal{L}_K \supset \frac{1}{2}\phi\Box\phi,
	\frac{1}{4}F^2_{\mn}, \frac{1}{2}m^2\phi^2,
	\frac{1}{2}\phi_1\Box\phi_2, \phi_1\partial_\mu A_\mu, \dots \]

    %%%%%%%%% B %%%%%%%%%%% 
    \item [Boltzmann distribution]  $n_{i} = Ne^{-\beta E_{i}}$

    %%%%%%%%% C %%%%%%%%%%% 
    \item [causality]
    \item [charge conjugation C] taking particles to antiparticles
	\[  C:\quad\psi\rightarrow-i\gamma_2\psi^*\equiv\psi_C	\]
	In the Weyl basis, $\gamma_2^*=-\gamma_2$ and $\gamma_2^T=\gamma_2$, so
	\[  C:\quad\psi^*\rightarrow-i\gamma_2\psi  \]
    \item [chirality] The handedness of a spinor is referred to as its
	chirality. The \textbf{left-handed} and \textbf{right-handed} 
	refer to the ($\frac{1}{2},0$) or (0,$\frac{1}{2}$) representations
	of the Lorentz group. This concept only exists for spinors, or more
	precisely for (A,B) representations of the Lorentz group with
	$A\neq B$. Almost always, chirality means that a theory is not
	symmetric between left-handed Weyl spinors $\psi_L$ and right-handed
	spinors $\psi_R$
    \item [cluster decomposition principle]
    \item [commutativity of addition and multiplication] 
	$a+b=b+a$ and $a\cdot b = b\cdot a$
    \item [contravariant vectors]   vectors with upper indices
    \item [covariant vectors]	vectors with lower indices

    %%%%%%%%% D %%%%%%%%%%% 
    \item [Dirac spinors]
    \item [Dirac Lagrangian] 
	\[
	    \mathcal{L}=\bar{\psi}(i\slashed{\partial}-m)\psi
	\]
    \item [Dirac equation]
	\[  
	    (i\slashed{D} -m)\psi =0	
	\]
    \item [Dirac Mass]
	\[  
	    \mathcal{L}_{\text{Dirac mass}} = m(\psi_L^\dag\psi_R + \psi^\dag_R\psi_L) 
	\]
    \item [Distributivity of multiplication over addition]
	$a\cdot(b+c)=(a\cdot b) + (a\cdot c)$

    %%%%%%%%% E %%%%%%%%%%% 
    \item [equipartion theorem] a body in thermal equilibrium should have
	energy equally distributed among all possible modes, (mode is a
	seperation of phase space), which means all modes have the same
	energy.

    %%%%%%%%% F %%%%%%%%%%% 
    \item [faithful representation] A representation in which each group
	element gets its own matrix is called a \emph{faithful
	representation}.
    \item [Fermi's golden rule]	$\Gamma \sim |\mathcal{M}|^{2}\delta(E_f - E_i)$
    \item [first principle]

    %%%%%%%%% G %%%%%%%%%%% 
    \item [Gauge transform] $\phi \rightarrow e^{-i\alpha}\phi$
    \item [good quantum number] which doesn't change along time. $[Q, H] = 0$
    \item [Grassmann Numbers] For Majorana masses to be non-trivial, fermion 
	compnents cannot be regular numbers, they must be anticommuting numbers. 
	Such things are called Grassmann numbers.

    %%%%%%%%% H %%%%%%%%%%% 
    \item [Helicity] spin projected on the direction of motion is called the
	helicity. $\hat{h}=\frac{\vec{\sigma}\cdot\vec{p}}{|\vec{p}|}$

    %%%%%%%%% L %%%%%%%%%%% 
    \item [Legendre transformation]
    \item [Levi-Civita] $\epsilon_{ijk} = \left\{
	\begin{aligned}
	    1\quad  normal order(123,231,312) \\
	    -1\quad reverse order(132,213,321)	\\
	    0\quad  otherwise	\\
	\end{aligned} \right.$
    \item [Lie algebra] the generators of the Lie group form an algebra
	called its Lie algebra. 
    \item [Lie groups]	Lie groups are a class of groups, including the
	Lorentz group, with an infinite number of elements but a finite
	number of generators.
    \item [lightlike]	$V^\mu V_\mu = 0$
    \item [little group] The representation of the full \Poincare{}
	group is induced by a representation of the subgorup of the
	\Poincare{} group that holds $p^\mu$ fixed, called the
	\emph{little group}. When $P_\mu$ is massive, the little group is
	SO(3); when $p_\mu$ is massless, the little group is ISO(2).
    \item [locality]
    \item [Lorentz group] this is the generalization of the rotation group
	to include both rotations and boosts.

    %%%%%%%%% M %%%%%%%%%%% 
    \item [Majorana spinor] A spinor whose antiparticle is itself. 
    \item [Majorana masses]
	\[
	    \mathcal{L}=i\psi^\dag_L\sigma_\mu\partial_\mu\psi_L+i\frac{m}{2}(\psi^\dag_L\sigma_2\psi^*_L-\psi^T_L\sigma_2\psi_L)
	\]
	The mass terms in this Lagrangian are called \textbf{Majorana masses}.
    \item [Majorana fermions]
	in Dirac spinors:
	\[
	    \psi=\begin{pmatrix}
		\psi_L	\\
		i\sigma_2\psi^*_L   \\
	    \end{pmatrix}
	\]

    %%%%%%%%% P %%%%%%%%%%% 
    \item [pseudo scalar] particles with odd \textbf{parity}

    %%%%%%%%% Q %%%%%%%%%%% 
    \item [quantize]	promote x and p as operators and impose the
	canonical commutation relations:    $[x, p] = i$
    \item [quantum process]  time evolution of an open quantum system ???

    %%%%%%%%% R %%%%%%%%%%% 
    \item [Rarita-Schwinger field]  spin-$\frac{3}{2}$
    \item [representation] A set of objects that mix under a transformation
	group is called a representation of the group, though technically
	the matrix embedding is the representation. A representation is a 
	particular embedding of group elements into operators that act on a 
	vector space. For finite-dimensional representations, this means an 
	embedding of the $g_i$ into matrices. 

    %%%%%%%%% S %%%%%%%%%%% 
    \item [second quantization]	canonical quantization of relativistic
	fields, 
	\[  H_0 = \int \frac{d^{3}p}{(2\pi)^3}\omega_p(a^{\dag}_p a_p +
	\frac{1}{2}) \] 
	First quantization refer to the discrete mode, for
	example, of a particle in a box. Second quantization refers to the
	integer numbers of excitations of each of these modes. There are two
	features in second quantization:
	\begin{enumerate}
	    \item We have many quantum mechanical systems - one for each
		$\vec{p}$ - all at the same time.
	    \item We interpret the nth excitation of the $\vec{p}$ harmonic
		oscillator as having n \emph{particles}.
	\end{enumerate}
    \item [S-matrix]
    \item [spacelike]	$V^\mu V_\mu < 0$
    \item [SO(n)] the group of nD rotations ($det(R) = 1$)
	
    %%%%%%%%% T %%%%%%%%%%% 
    \item [timelike]	$V^\mu V_\mu > 0$

    %%%%%%%%% U %%%%%%%%%%% 
    \item [unitary] $\Lambda^{\dag}\Lambda = 1$

    %%%%%%%%% W %%%%%%%%%%% 
    \item [Weyl spinor] Irreducible unitary spin-$\frac{1}{2}$
	representations of the \Poincare{} group.

    %%%%%%%%% $\gamma$ %%%%%%%%%%% 
    \item [$\gamma$ matrix]
	In the Weyl basis:
	\[  \gamma_\mu = 
	    \begin{pmatrix}
		0   & \sigma_\mu    \\
		\bar{\sigma}_\mu  & 0	\\
	    \end{pmatrix} 
	\]
    \item [$\gamma^5$]
	\[
	    \gamma^5 \equiv i\gamma^0\gamma^1\gamma^2\gamma^3
	\]
	In the Weyl representation:
	\[
	    \gamma^5 = 
	    \begin{pmatrix}
		-\mathcal{1}	&   \\
		    & \mathcal{1}   \\
	    \end{pmatrix}
	\]
\end{description}
